Footpath Planning for Example-driven Procedural Road Networks

### 2020-03-18 paper/paper.tex
Fix titles
Add Douglas-Peucker algorithm

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage{hyperref}
\usepackage{multicol}
\setlength\parindent{0pt}

@@

\section(The geodata used in this project)

@@

\subsection(OSM Data)

@@

\subsection(SLU Data)

@@

\subsection(A word on coordinate systems)

@@

//TODO: Algorithm of Douglas-Peucker

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage[ruled,vlined]{algorithm2e}
\setlength\parindent{0pt}

@@

\section{The geodata used in this project}

@@

\subsection{OSM Data}

@@

\subsection{SLU Data}

@@

\subsection{A word on coordinate systems}

@@

\begin{algorithm}[H]
\SetAlgoLined
\KwResult{Write here the result }
    // Find the point with the maximum distance\;
    $d_{max}$ = 0\;
    $index$ = 0\;
    $end$ = length(PointList)\;

    \For{$i$=2 to ($end$-1)}{
        $d$ = perpendicularDistance(PointList[$i$], Line(PointList[1], PointList[$end$]))\;
        \If{$d$ $>$ $d_{max}$} {
            $index$ = $i$\;
            $d_{max}$ = $d$\;
        }
    }

    ResultList = []\;

    // If max distance is greater than epsilon, recursively simplify\;
    \eIf{$d_{max}$ $>$ $\epsilon$} {
        // Recursive call\;
        recResults1[] = Douglas-Peucker(PointList[1...$index$], $\epsilon$)\;
        recResults2[] = Douglas-Peucker(PointList[$index$...$end$], $\epsilon$)\;

        // Build the result list\;
        ResultList[] = {recResults1[1...length(recResults1) - 1], recResults2[1...length(recResults2)]}\;
    }{
        ResultList[] = {PointList[1], PointList[$end$]}\;
    }
    \Return{ResultList[]}\;

    \caption{Douglas-Peucker}
\end{algorithm}
